\LARGE \bf Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-03-25 manuscript.tex
fix; prof. comments

\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{1}$% <-this % stops a space
\thanks{*This work was supported by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}}% <-this % stops a space
\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
\thanks{$^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
        {\tt\small jiyun6606@gm.gist.ac.kr}}%
}

@@

% One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
One of the common issues in using NNs 
\color{red}
for control compontnets
\color{black}
is that the outputs of NNs are not predictable.
This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
\color{red}
This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control conponents from NNs.
\color{black}
\st{
    This issue should be addressed for safety because the unpredictable control input may reach the actuator's physical limitations and result in system collapse.
}

@@

To approximate the desired controller, an NN is utilized.
\color{red}
    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2017aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
\color{black}
The NN with a single hidden layer is represented as 
\begin{equation}
    \NN({\q_{n}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{n}})
    ,
\end{equation}
where ${\q_{n}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ \forall i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i},\ \forall i\in\{0,1\}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i:=(l_i+1)\cdot l_{i+1},\ \forall i\in\{0,1\}$ and $\Xi:=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.

@@

\color{red}
    As discussed in Section \ref{sec:intro}, the boundedness of the weights should be considered to prevent excessively large control inputs and system instability.
\color{black}
For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}:=c_{\theta_i}(\estwth_i)=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ \forall i\in\{0,1\}$.
The control problem can be reformulated into a constrained optimization problem as follows:
\begin{equation}
    \begin{matrix}
        \min_{{\estwth}} \ J(\mv \xi;{\estwth})
        :=
        \tfrac{1}{2}
        \mv \xi^\top \mm \Lambda \mv \xi
        \\ \\
        \begin{aligned}
        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
        := 
        \{\theta_0,\theta_1\}
        ,
        \end{aligned}
    \end{matrix}
\end{equation}
where $\mm \Lambda=\mm \Lambda^\top >0$ denotes the weighting matrix.
In this optimization problem, $\mv \xi$ is considered a predefined parameter.
The corresponding Lagrangian function is defined as
\begin{equation}
    L(
        \mv \xi,
        {\estwth},
        [\lambda_j]_{j\in\mathcal I}
    )
    := 
    J(\mv \xi;{\estwth})
    +
    \textstyle\sum_{j\in\mathcal I} \lambda_jc_j({\estwth})
    .
\end{equation}
% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L(\mv \xi,{\estwth},[\lambda_j]_{j\in\mathcal I}$, the adaptation law is derived as follows:
\begin{subequations}
    \begin{align}
            \ddtt {{\estwth}}
            &
            =
            -\alpha 
            \pptfrac{L}{{\estwth}}
            =-\alpha 
            \left(
                \pptfrac{J}{{\estwth}}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq. adaptation law th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j
            \pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad\quad\quad\quad      \      
            \forall j\in\mathcal I,
        \label{eq. adaptation law L}
            \\
            \lambda_j 
            & 
            = 
            \max(\lambda_j,0) ,
        \label{eq. adaptation law L max}
    \end{align}
    \label{eq. adaptation laws}
\end{subequations}
where arguments of $L$ are suppressed for brevity, and $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
\color{red}
% The Eq.~\eqref{eq. adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
\color{black}

@@

The dynamics of ${\mm \eta}_0$ and ${\estwth}_0$ are represented as
\begin{equation}
    \begin{aligned}     
        \ddtt{\mm \eta}_0 =& 
        \mm A_\xi{\mm \eta}_0 -\mm B_\xi 
        \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )
        \\
        \ddtt{{\estwth}}_0
        =&
        -\alpha 
        (
            {\mm \eta}_0^\top \mm \Lambda\mv \xi+2\lambda_{\theta_0} {\estwth}_0
        )
        .
    \end{aligned}
\end{equation}
According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $\norm{-\mm B_\xi\estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )}$ is bounded.
To obtain the invariance set of ${\estwth}_0$, taking the time derivative of the Lyapunov function $V_0=\tfrac{1}{2\alpha}{\estwth}_0^\top {\estwth}_0$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt {V}_0 =& 
        -{\estwth}_0^\top (
            {\mm \eta}_0\mm \Lambda\mv \xi 
            +2\lambda_{\theta_0}{\estwth}_0
        )
        \\
        \le &
        \norm{{\estwth}_0} \norm{{\mm \eta}_0\mm \Lambda\mv \xi} 
        -
        2\lambda_{\theta_0} {\estwth}_0^\top {\estwth}_0
        ,
        \\
        \le &
        -2\lambda_{\theta_0} 
        \norm{{\estwth}_0}^2 
        + 
        \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
        \norm{{\estwth}_0}
        .
    \end{aligned}
\end{equation}
Then, the invariance set can be represented as 
\begin{equation}
    \Theta_{{\theta}_0} :=
    \left\{
        {\estwth}_0\mid\norm{\estwth_0}
        \le
        \tfrac{
            \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
        }{
            2\lambda_{\theta_0}
        }
    \right\}
    .    
\end{equation}
If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{{\theta}_0}$ converges to $\{{\estwth}_0 \mid \norm{{\estwth}_0} \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
Therefore, the Lagrange multiplier $\lambda_{\theta_0}$ is also bounded.

@@

All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=\mm I_2$ and $\mm \Lambda=\mydiag([5,1,15,15])$.
The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
\color{red}    
    The validity of the selected number of nodes were demonstrated through experiments 
\color{black}
The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{n}=(\qd^\top ,1)^\top $.
For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
The sampling time of the simulation and the simulation termination time were set to $T_s=100\,\mu\mathrm{s}$ and $T=10\,\mathrm{s}$, respectively.

@@

\begin{figure}[!t]      
    \centering
        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig9.eps}%
        \label{fig: weight NAC-L2}}
    \vspace{.1mm}
        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig10.eps}%
        \label{fig: weight NAC-eMod}}
    \vspace{.1mm}
        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig8.eps}%
        \label{fig: weight NAC-CO}}
    \caption{Weight norms of NAC-L2, NAC-eMod, and NAC-CO.}
    \label{fig: weight}
\end{figure}

\begin{figure}[!t]      
    \centering
        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig6.eps}%
        \label{fig: error NAC-L2}}
    \vspace{.1mm}
        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig7.eps}%
        \label{fig: error NAC-eMod}}
    \vspace{.1mm}
        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig5.eps}%
        \label{fig: error NAC-CO}}
    \caption{Tracking errors of NAC-L2, NAC-eMod, and NAC-CO.}
    \label{fig: error}
\end{figure}

@@

\begin{figure}[!t]      
    \centering
        \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig/fig12.eps}%
        \label{fig: weight per layer NAC-CO}}
    \vspace{.1mm}
        \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig/fig11.eps}%
        \label{fig: multipliers NAC-CO}}
        \caption{Weight norms and Lagrange multipliers of NAC-CO ($\beta=0.001$).}
        \label{fig: weight and multiplier}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\footnotesize
    \bibliographystyle{ieeetr}
    \bibliography{dding_template/refs}
}

>>>>

\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{3}$% <-this % stops a space
\thanks{
    *This work was supported in part by a Korea Research Institute for Defense Technology planning and advancement (KRIT) grant funded by Korea government DAPA (Defense Acquisition Program Administration) (No. KRIT-CT-22-087, Synthetic Battlefield Environment based Integrated Combat Training Platform) and in part by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}
}% <-this % stops a space
\thanks{
    $^{1}$Myeongseok Ryu is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr}
}%
\thanks{
    $^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
        {\tt\small jiyun6606@gm.gist.ac.kr}
}%
\thanks{
    $^{3}$Kyunghwan Choi was with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, Republic of Korea. He is currently with the Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Republic of Korea {\tt\small kyunghwan.choi90@gmail.com}
}%
}

@@

% One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
One of the common issues in using NNs as control compontnets is that the outputs of NNs are not predictable.
This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control conponents from NNs.

@@

To approximate the desired controller, an NN is utilized.
Even though DNNs have a higher approximation capability than SHLNNs \cite{Rolnick:2018aa}, here, an SHLNN is utilized for simplicity and low computational complexity.
The NN with a single hidden layer is represented as 
\begin{equation}
    \NN({\q_{n}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{n}})
    ,
\end{equation}
where ${\q_{n}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ \forall i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i},\ \forall i\in\{0,1\}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i:=(l_i+1)\cdot l_{i+1},\ \forall i\in\{0,1\}$ and $\Xi:=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.

@@

As discussed in Section \ref{sec:intro}, the boundedness of the weights should be considered to prevent excessively large control inputs and system instability.
For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}:=c_{\theta_i}(\estwth_i)=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ \forall i\in\{0,1\}$.
The control problem can be reformulated into a constrained optimization problem as follows:
\begin{equation}
    \begin{matrix}
        \min_{{\estwth}} \ J(\mv \xi;{\estwth})
        :=
        \tfrac{1}{2}
        \mv \xi^\top \mm \Lambda \mv \xi
        \\ \\
        \begin{aligned}
        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
        := 
        \{\theta_0,\theta_1\}
        ,
        \end{aligned}
    \end{matrix}
\end{equation}
where $\mm \Lambda=\mm \Lambda^\top >0$ denotes the weighting matrix.
In this optimization problem, $\mv \xi$ is considered a predefined parameter.
The corresponding Lagrangian function is defined as
\begin{equation}
    L(
        \mv \xi,
        {\estwth},
        [\lambda_j]_{j\in\mathcal I}
    )
    := 
    J(\mv \xi;{\estwth})
    +
    \textstyle\sum_{j\in\mathcal I} \lambda_jc_j({\estwth})
    .
\end{equation}
% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L(\mv \xi,{\estwth},[\lambda_j]_{j\in\mathcal I}$, the adaptation law is derived as follows:
\begin{subequations}
    \begin{align}
            \ddtt {{\estwth}}
            &
            =
            -\alpha 
            \pptfrac{L}{{\estwth}}
            =-\alpha 
            \left(
                \pptfrac{J}{{\estwth}}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq. adaptation law th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j
            \pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad\quad\quad\quad      \      
            \forall j\in\mathcal I,
        \label{eq. adaptation law L}
            \\
            \lambda_j 
            & 
            = 
            \max(\lambda_j,0) ,
        \label{eq. adaptation law L max}
    \end{align}
    \label{eq. adaptation laws}
\end{subequations}
where arguments of $L$ are suppressed for brevity, and $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
\color{red}
% The Eq.~\eqref{eq. adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
\color{black}

@@

The dynamics of ${\mm \eta}_0$ and ${\estwth}_0$ are represented as
\begin{equation}
    \begin{aligned}     
        \ddtt{\mm \eta}_0 =& 
        \mm A_\xi{\mm \eta}_0 -\mm B_\xi 
        \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )
        ,
        \\
        \ddtt{{\estwth}}_0
        =&
        -\alpha 
        (
            {\mm \eta}_0^\top \mm \Lambda\mv \xi+2\lambda_{\theta_0} {\estwth}_0
        )
        .
    \end{aligned}
\end{equation}
According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $\norm{-\mm B_\xi\estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )}$ is bounded.
To obtain the invariance set of ${\estwth}_0$, taking the time derivative of the Lyapunov function $V_0=\tfrac{1}{2\alpha}{\estwth}_0^\top {\estwth}_0$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt {V}_0 =& 
        -{\estwth}_0^\top (
            {\mm \eta}_0\mm \Lambda\mv \xi 
            +2\lambda_{\theta_0}{\estwth}_0
        )
        \\
        \le &
        \norm{{\estwth}_0} \norm{{\mm \eta}_0\mm \Lambda\mv \xi} 
        -
        2\lambda_{\theta_0} {\estwth}_0^\top {\estwth}_0
        ,
        \\
        \le &
        -2\lambda_{\theta_0} 
        \norm{{\estwth}_0}^2 
        + 
        \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
        \norm{{\estwth}_0}
        .
    \end{aligned}
\end{equation}
Then, the invariance set can be represented as 
% \begin{equation}
$
    \Theta_{{\theta}_0} :=
    % \left\{
    \{
        {\estwth}_0\mid\norm{\estwth_0}
        \le
        \tfrac{
            \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
        }{
            2\lambda_{\theta_0}
        }
    % \right\}
    \}
    .    
$
% \end{equation}
If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{{\theta}_0}$ converges to $\{{\estwth}_0 \mid \norm{{\estwth}_0} \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
Therefore, the Lagrange multiplier $\lambda_{\theta_0}$ is also bounded.

@@

All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=\mm I_2$ and $\mm \Lambda=\mydiag([5,1,15,15])$.
The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
The validity of the selected number of nodes were demonstrated through experiments 
The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{n}=(\qd^\top ,1)^\top $.
For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
The sampling time of the simulation and the simulation termination time were set to $T_s=100\,\mu\mathrm{s}$ and $T=10\,\mathrm{s}$, respectively.

@@

\begin{figure}[!t]      
    \centering
        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig9.eps}%
        \label{fig: weight NAC-L2}}
    \vspace{-2mm}
        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig10.eps}%
        \label{fig: weight NAC-eMod}}
    \vspace{-2mm}
        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig8.eps}%
        \label{fig: weight NAC-CO}}
    \caption{Weight norms of NAC-L2, NAC-eMod, and NAC-CO.}
    \label{fig: weight}
\end{figure}

\begin{figure}[!t]      
    \centering
        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig6.eps}%
        \label{fig: error NAC-L2}}
    \vspace{-2mm}
        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig7.eps}%
        \label{fig: error NAC-eMod}}
    \vspace{-2mm}
        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig5.eps}%
        \label{fig: error NAC-CO}}
    \caption{Tracking errors of NAC-L2, NAC-eMod, and NAC-CO.}
    \label{fig: error}
\end{figure}

@@

\begin{figure}[!t]      
    \centering
        \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig/fig12.eps}%
        \label{fig: weight per layer NAC-CO}}
    \vspace{-1mm}
        \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig/fig11.eps}%
        \label{fig: multipliers NAC-CO}}
        \caption{Weight norms and Lagrange multipliers of NAC-CO ($\beta=0.001$).}
    \vspace{-2mm}
        \label{fig: weight and multiplier}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% {\footnotesize
    \bibliographystyle{ieeetr}
    \bibliography{dding_template/refs}
% }
